---
title: "Project"
author: "Karthik, Shrujan And Shubham"
date: "2022-12-02"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse) 
library(readr)
library(dplyr)
library(magrittr)
library(Metrics)
library(pROC)
library(precrec) 
library(ROSE) 
library(nnet) 
library(randomForest)
```


```{r}
data = read.csv("/Users/ricky/Downloads/Archive/insurance_claims.csv")
data = data[,c(-25,-40)] # delete variables
data = data %>% mutate_if(is.character,as.factor)
data = as.data.frame(data)
round(prop.table(table(data$fraud_reported)),2)
```


#months_as_customer - continuous data - with no outliers almost normal distribution(right skew)
```{r}

summary(data$months_as_customer)
boxplot(data$months_as_customer)
hist(data$months_as_customer)
ggplot(data)+geom_bar(aes(x=months_as_customer, fill=fraud_reported))
```

#age - continous data - Mean almost equal to median - close to normal distribution(right skew)
```{r}
summary(data)
summary(data$age)
boxplot(data$age)
hist(data$age)
ggplot(data)+geom_bar(aes(x=age, fill=fraud_reported))


```

#policy_number - continous data - Mean almost equal to median - close to normal distribution(right skew)
```{r}
summary(data$policy_number)
boxplot(data$policy_number)
hist(data$policy_number)
ggplot(data)+geom_bar(aes(x=policy_number, fill=fraud_reported))

```

#policy_bind_date - discrete - not apt
```{r}
summary(data$policy_bind_date)
plot(data$policy_bind_date)
```

#state - discrete - to understand which state has more 
```{r}
summary(data$policy_state)
plot(data$policy_state)
ggplot(data)+geom_bar(aes(x=policy_state, fill=as.factor(fraud_reported)))

```

#policy_csl - discrete - which policy - 250/500 has been the usual policy
```{r}
summary(data$policy_csl)
plot(data$policy_csl)
ggplot(data)+geom_bar(aes(x=policy_csl, fill=as.factor(fraud_reported)))
```

#policy_deductable - continous - Close to normal with a right skew
```{r}
summary(data$policy_deductable)
boxplot(data$policy_deductable)
hist(data$policy_deductable)
ggplot(data)+geom_bar(aes(x=policy_deductable, fill=fraud_reported))
```


#policy_annual_premium - Close to normal distribution with a left skew also has some outliers 
```{r}
summary(data$policy_annual_premium)
boxplot(data$policy_annual_premium)
hist(data$policy_annual_premium)
ggplot(data)+geom_bar(aes(x=policy_annual_premium, fill=fraud_reported))
```


#umbrella_limit - here the median is 0. Outliers exist
```{r}
summary(data$umbrella_limit)
boxplot(data$policy_annual_premium)
hist(data$policy_annual_premium)
ggplot(data)+geom_bar(aes(x=umbrella_limit, fill=fraud_reported))
```

#insured_zip - This is a right skew with no outliers- 
```{r}

summary(data$insured_zip)
boxplot(data$insured_zip)
hist(data$insured_zip)
ggplot(data)+geom_bar(aes(x=insured_zip, fill=fraud_reported))
```
#insured_sex - Discrete - Females claimed more.
```{r}
summary(data$insured_sex)
plot(data$insured_sex)
ggplot(data)+geom_bar(aes(x=insured_sex, fill=as.factor(fraud_reported)))
```
#insured_education_level - Discrete - JD and high school have claimed more 
```{r}
summary(data$insured_education_level)
plot(data$insured_education_level)
ggplot(data)+geom_bar(aes(x=insured_education_level, fill=as.factor(fraud_reported)))

```

#occupation - discrete - Which occupation usually claims more. 
```{r}
summary(data$insured_occupation)
plot(data$insured_occupation)
ggplot(data)+geom_bar(aes(x=insured_occupation, fill=as.factor(fraud_reported)))

```

#insured_hobbies - discrete - hobbies of claimed people. - Not necessary.
```{r}

summary(data$insured_hobbies)
plot(data$insured_hobbies)
ggplot(data)+geom_bar(aes(x=insured_hobbies, fill=as.factor(fraud_reported)))
```
#insured_relationship - discrete - Helps to know dependencies.
```{r}
summary(data$insured_relationship)
plot(data$insured_relationship) 
ggplot(data)+geom_bar(aes(x=insured_relationship, fill=as.factor(fraud_reported)))

```


#capital.gains - continuos - with a median 0 and no outliers
```{r}
summary(data$capital.gains)
boxplot(data$capital.gains) 
hist(data$capital.gains)
ggplot(data)+geom_bar(aes(x=capital.gains, fill=fraud_reported))
```
#capital.loss - continuous - Left skew with no outliers
```{r}
summary(data$capital.loss)
boxplot(data$capital.loss) 
hist(data$capital.loss)
ggplot(data)+geom_bar(aes(x=capital.loss, fill=fraud_reported))
```

#incident_date  - discrete - may vary - not important
```{r}
summary(data$incident_date)
plot(data$incident_date) 
ggplot(data)+geom_bar(aes(x=incident_date, fill=as.factor(fraud_reported)))
```

#incident_type  - discrete - to know the what happened to the vehicle 
```{r}

summary(data$incident_type)
plot(data$incident_type)
ggplot(data)+geom_bar(aes(x=incident_type, fill=as.factor(fraud_reported)))
```

#collision type - with an unknown value about where it collided.
```{r}
summary(data$collision_type)
plot(data$collision_type)
ggplot(data)+geom_bar(aes(x=collision_type, fill=as.factor(fraud_reported)))
```

#incident_severity - discrete - About how bad the damage is:
```{r}
summary(data$incident_severity)
plot(data$incident_severity)
ggplot(data)+geom_bar(aes(x=incident_severity, fill=as.factor(fraud_reported)))

```

#authorities_contacted - if the autorities are contacted and which one.
```{r}
summary(data$authorities_contacted)
plot(data$authorities_contacted)
ggplot(data)+geom_bar(aes(x=authorities_contacted, fill=as.factor(fraud_reported)))
```

#incident_state - discrete - Which state has the incident occurred ? 
```{r}
summary(data$incident_state)
plot(data$incident_state)
ggplot(data)+geom_bar(aes(x=incident_state, fill=as.factor(fraud_reported)))
```
#incident_city - discrete - Which city has the incident occurred ? 
```{r}
summary(data$incident_city)
plot(data$incident_city)
ggplot(data)+geom_bar(aes(x=incident_city, fill=as.factor(fraud_reported)))
```
#number_of_vehicles_involved - Right skew with no outliers 
```{r}
summary(data$number_of_vehicles_involved)
boxplot(data$number_of_vehicles_involved)
hist(data$number_of_vehicles_involved)
ggplot(data)+geom_bar(aes(x=number_of_vehicles_involved, fill=fraud_reported))
```

#property_damage - With an unknown value 
```{r}
summary(data$property_damage)
plot(data$property_damage)
ggplot(data)+geom_bar(aes(x=property_damage, fill=as.factor(fraud_reported)))
```


#Bodily_Injured - continuous - with no outliers and left skew.
```{r}
summary(data$bodily_injuries)
boxplot(data$bodily_injuries)
hist(data$bodily_injuries)
ggplot(data)+geom_bar(aes(x=bodily_injuries, fill=fraud_reported))

```

#witnesses - continuous With a right skew with no outliers
```{r}
summary(data$witnesses)
boxplot(data$witnesses)
hist(data$witnesses)
ggplot(data)+geom_bar(aes(x=witnesses, fill=fraud_reported))

```
#police_report_available - Discrete 
```{r}
summary(data$police_report_available)
plot(data$police_report_available)
ggplot(data)+geom_bar(aes(x=police_report_available, fill=as.factor(fraud_reported)))
```

#total_claim_amount - continuous - Left Skew with a few outliers
```{r}
summary(data$total_claim_amount)
boxplot(data$total_claim_amount)
hist(data$total_claim_amount)
ggplot(data)+geom_bar(aes(x=total_claim_amount, fill=fraud_reported))
```
#injury_claim - continuous -with 0 outliers and a right skew
```{r}
summary(data$injury_claim)
boxplot(data$injury_claim)
hist(data$injury_claim)
ggplot(data)+geom_bar(aes(x=injury_claim, fill=fraud_reported))


```

#property_claim -contunuius - Right skew with outliers
```{r}
summary(data$property_claim)
boxplot(data$property_claim)
hist(data$property_claim)

ggplot(data)+geom_bar(aes(x=property_claim, fill=fraud_reported))

```
#vehicle_claim - continious - 0 outliers with a left skew
```{r}
summary(data$vehicle_claim)
boxplot(data$vehicle_claim)
hist(data$vehicle_claim)
ggplot(data)+geom_bar(aes(x=vehicle_claim, fill=fraud_reported))
```


#auto_make - discrete - 
```{r}
summary(data$auto_make)
plot(data$auto_make)
ggplot(data)+geom_bar(aes(x=auto_make, fill=as.factor(fraud_reported)))

```

#auto_model - discrete - Which model is usually claimed
```{r}
summary(data$auto_model)
plot(data$auto_model)
ggplot(data)+geom_bar(aes(x=auto_model, fill=as.factor(fraud_reported)))

```
#auto_year - Perfect normal distribution with mean = median 
```{r}

summary(data$auto_year)
boxplot(data$auto_year)
hist(data$auto_year)
ggplot(data)+geom_bar(aes(x=auto_year, fill=fraud_reported))

```
